---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r pkg-knitr-opts, include=FALSE}
hrbrpkghelpr::global_opts()
```

```{r badges, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::stinking_badges()
```

```{r description, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::yank_title_and_description()
```

## WIP

Definitely a WIP (drop some code for some credit!), and _p(sherlocked)_ ~= `0.7` but it's been a while since I made a public R package.

## What's Inside The Tin

The following functions are implemented:

```{r ingredients, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::describe_ingredients()
```

## Installation

```{r install-ex, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::install_block()
```

## Usage

```{r lib-ex}
library(webfinger)

# current version
packageVersion("webfinger")

```

Basic `acct` usage:

```{r ex-01}
webfinger("acct:hrbrmstr@rud.is")
```

```{r ex-01a}
webfinger("acct:hrbrmstr@infosec.exchange")
```

Some endpoints are friendlier than others (but you should generally prepend `acct:` to be safe):

```{r ex-02}
webfinger("hrbrmstr@mastodon.social")
```

And, there exists 'proxy' webfinger services like this one for the bird site:

```{r ex-03}
wf("acct:hrbrmstr@twitter.com", host = "twitter-webfinger.appspot.com")
```

## webfinger Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```
